\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Jehu Zepeda-Silva} \\ \vspace{1pt}
    \small 408-807-5334 $|$ \href{mailto:x@x.com}{\underline{jehuzepedasilva@berkeley.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/jehuzepedasilva}} $|$
    \href{https://github.com/...}{\underline{github.com/jehuzepedasilva}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Berkeley}{Berkeley, CA}
      {Bachelor of Arts in Computer Science}{May 2024}
      \begin{itemize}[leftmargin=0in, label={}]
        \small{\item{
         \textbf{Relevant Coursework}{: Great Ideas in Computer Architecture, Principles and Techniques of Data Science, Introduction to Database Systems, Efficient Algorithms and Intractable Problems, Introduction to Artificial Intellegence.} \\
        }}
  \resumeSubHeadingListEnd
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Inventory and Operations Manager}{May 2018 -- Present}
      {Summit Store}{Los Gatos, CA}
      \resumeItemListStart
        \resumeItem{Managed and coordinated all inventory operations, ensuring timely and accurate delivery schedules.}\\
        \resumeItem{Supervised and led a team responsible for maintaining well-stocked and organized inventory.}\\
        \resumeItem{Oversaw the ordering process, ensuring optimal stock levels and minimizing waste.}\\
        \resumeItem{Ensured accurate and up-to-date pricing aligned with profit margin goals.}\\
        \resumeItem{Maintained accurate and comprehensive item records in the system for efficient scanning and checkout.}\\
        \resumeItem{Conducted end-of-day financial reconciliations, ensuring all cash transactions were accurately recorded and secured in the safe.}\\
        \resumeItem{Utilized inventory management software to track and analyze stock levels, sales trends, and forecast demand.}\\
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NGordNet} $|$ \emph{Java}}{Spring 2023}
            \resumeItemListStart
            \resumeItem{Developed a web based application designed to facilitate the exploration of the historical usage of English words.}
            \resumeItem{Employed Depth-First search and Breadth-First search to identify hyponyms and hypernyms of a large data set.}
      \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Spam and Ham} $|$ \emph{Python, Scikit-Learn, Matplotlib, NumPy}}{Fall 2023}
            \resumeItemListStart
            \resumeItem{Build and trained a logistic regression model to classify emails as spam, or ham (non-spam).}
            \resumeItem{Created visulazations to find features within the data set, in order to accurately classify.}
            \resumeItem{Achieved an overall accuracy of 90\% in classifying emails.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Guitar Hero Lite} $|$ \emph{Java}}{Spring 2023}
            \resumeItemListStart
            \resumeItem{Created a guitar synthesizer with the ability to read input from the keyboard.}
            \resumeItem{Using a string synthesis algorithm, the program outputted a musical note.}
        \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{CPU} $|$ \emph{Logisim}}{Summer 2023}
            \resumeItemListStart
            \resumeItem{Developed a fully functioning pipelined single-cylce CPU.}
            \resumeItem{Read in Assembly instructions with ability to work with saved input on 32-bit registers.}
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Exploring Cook County, Illinois Housing} $|$ \emph{Python, NumPy}}{Fall 2023}
            \resumeItemListStart
            \resumeItem{Conducted reasearch on Cook County's property tax data.}
            \resumeItem{Discovered racial bias in the way property was being taxed, favoring the wealthy over lower-income households.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{AI Driven Pac-Man} $|$ \emph{Python, NumPy}}{Spring 2024}
            \resumeItemListStart
            \resumeItem{Implemented Pac-Man using four AI-Techniques (state-space search, probabilistic inference, reinforcement learning, logical inference) improving Pac-Man's problem-solving efficiency by 10\%.}
            \resumeItem{Improved game navigation and agent decision-making using search algorithms and reinforcement learning models (Value Iteration, Q-Learning, Approximate Q-Learning), resulting in a 2x increase in game completion rate.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML, CSS, JavaScript, Node.js, Java, Python, C/C++, SQL} \\
     \textbf{Libraries}{: Pandas, NumPy, Scikit-Learn, Matplotlib, PyTorch}\\
     \textbf{Spoken Languages}{: Fluent in English and Spanish}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}